---
title: "Experiment 1 Qual Analysis"
author: "Cindy Xiong"
date: "April 9, 2019"
output:
  html_document:
    code_folding: hide
    fig_height: 6
    fig_width: 8
    highlight: pygments
    theme: yeti
    toc: yes
    toc_float: yes
  pdf_document:
    toc: yes
  word_document:
    toc: yes
always_allow_html: yes
---
```{r hide-messages}
library(knitr)
opts_chunk$set(warning = FALSE, message = FALSE, comment = FALSE)
```

Uploading appropriate libraries

```{r library, warnings=FALSE, warning=FALSE, message=FALSE}
# include packages
library(tidyr)
library(dplyr)
library(heplots)
library(MANOVA.RM)
library(multcomp)
library(lme4)
library(stringr)
library(ggplot2)
# package for Chi-Square
library(MASS)    
```

<h1> Qual Rating </h1>

```{r}
exp1QualRate <- read.csv("exp1_qual_ratings_free_response.csv")

# turn into long table
exp1QualRate_long <- gather(exp1QualRate, design, response, cluttered, decluttered, focused)
exp1QualRate_long <- exp1QualRate_long %>% 
  filter(category != "ignoreThis") 
```

Visualize by sentiment, design, topic

```{r table-sentiment-design-topic}
# note this is count data for qual, so "n" is going to be imbalanced
exp1QualRate_long %>% 
  group_by(sentiment, design, category) %>%
  summarise(n = n(), 
            rating = mean(response),
            se = sd(response)/sqrt(n())) 
```


```{r}
exp1QualRate_long %>% 
  group_by(sentiment, design, category) %>%
  summarise(n = n(), 
            rating = mean(response),
            se = sd(response)/sqrt(n())) %>% 
  ggplot(aes(x = design, y = rating, fill = design,
             ymin = rating - se * 1.96, 
             ymax = rating + se * 1.96)) +
  geom_bar(stat = "identity",
           width = 0.4) + 
  # error bars
  geom_errorbar(width = 0.1,
                position = position_dodge(0.5)) + 
  facet_grid(vars(sentiment), vars(category)) +
  # label axis
  labs(x = "design",
       y = "frequency") 
```

Aesthetics only (change "filter(category == "aesthetic" " to other category for closer examination")

```{r table-sentiment-design}
# note this is count data for qual, so "n" is going to be imbalanced
exp1QualRate_long %>% 
  filter(category == "aesthetic") %>%
  group_by(sentiment, design) %>%
  summarise(n = n(), 
            rating = mean(response),
            se = sd(response)/sqrt(n()))
```


```{r}
exp1QualRate_long %>% 
  filter(category == "aesthetic") %>%
  group_by(sentiment, design) %>%
  summarise(n = n(), 
            rating = mean(response),
            se = sd(response)/sqrt(n())) %>% 
  ggplot(aes(x = design, y = rating, fill = design,
             ymin = rating - se * 1.96, 
             ymax = rating + se * 1.96)) +
  geom_bar(stat = "identity",
           width = 0.4) + 
  # error bars
  geom_errorbar(width = 0.1,
                position = position_dodge(0.5)) + 
  facet_wrap(~sentiment) +
  # label axis
  labs(x = "design",
       y = "frequency") 
```

Analysis

b0 - aesthetics, negative, cluttered
b1 - aesthetics, positive, cluttered
b2 - aesthetics, negative, decluttered
b3 - aesthetics, negative, focused
b4 - clarity, negative, cluttered
b5 - professionalism, negative, cluttered
b6 - trustworthiness, negative, cluttered
b7 - aesthetics, positive, decluttered
b8 - aesthetics, positive, focused
b9 - clarity, positive, cluttered
b10 - professionalism, positive, cluttered
b11 - trustworthiness, positive, cluttered
b12 - clarity, negative, decluttered
b13 - claarity, negative, focused
b14 - professionalism, negative, decluttered,
b15 - professionalism, negative, focused
b16 - trustworthiness, negative, decluttered
b17 - trustworthiness, negative, focused
b18 - clarity, positive, decluttered
b19 - clarity, positive, focused
b20 - professionalism, positive, decluttered
b21 - professionalism, positive, focused
b22 - trustworthiness, positive, decluttered
b23 - trustworthiness, positive, focused

```{r}
model <- glm(response ~ sentiment * design * category, family=binomial(logit), data = exp1QualRate_long)
summary(model)

```


```{r}
model <- glm(response ~ sentiment * design, family=binomial(logit), 
             data = subset(exp1QualRate_long, exp1QualRate_long$category== "aesthetic"))
summary(model)
Anova(model)
exp(coef(model))
```

```{r}

model <- glm(response ~ sentiment * design, family=binomial(logit), 
             data = subset(exp1QualRate_long, exp1QualRate_long$category== "clarity"))
summary(model)
Anova(model)
exp(coef(model))
```

```{r}
model <- glm(response ~ sentiment * design, family=binomial(logit), 
             data = subset(exp1QualRate_long, exp1QualRate_long$category== "professionalism"))
Anova(model)
exp(coef(model))
```

```{r}
model <- glm(response ~ sentiment * design, family=binomial(logit), 
             data = subset(exp1QualRate_long, exp1QualRate_long$category== "trustworthiness"))
summary(model)
Anova(model)
```


