---
title: "PilotPowerAnalysis"
author: "Cindy Xiong"
date: "April 9, 2019"
output:
  html_document:
    code_folding: hide
    fig_height: 6
    fig_width: 8
    highlight: pygments
    theme: yeti
    toc: yes
    toc_float: yes
  pdf_document:
    toc: yes
  word_document:
    toc: yes
always_allow_html: yes
---

Uploading appropriate libraries

```{r library, warnings=FALSE, warning=FALSE, message=FALSE}
# include packages
library(tidyverse)
library(MANOVA.RM)
library(multcomp)
library(lme4)
library(stringr)
library(ggplot2)
```

Load data

```{r load-data}
pilot <- read.csv("pilot_quant.csv")
pilot$Cluttered <- 0
pilot$Decluttered <- 0
pilot$Focused <- 0
pilot$designdummy<-0

pilot$Cluttered[pilot$design=="Cluttered"]<-1
pilot$Decluttered[pilot$design=="Decluttered"]<-1
pilot$Focused[pilot$design=="Focused"]<-1

pilot$designdummy[pilot$design=="Cluttered"] <- 1
pilot$designdummy[pilot$design=="Decluttered"] <- 2
pilot$designdummy[pilot$design=="Focused"] <- 3

# create a long table with participant data in one column
pilot_long <- gather(pilot,p,data,s1,s2,s3,s4,s5,s6,s7,s8,s9,s10,s11,s12,s13,s14,s15,s16,s17)
pilot_long$p <- str_split_fixed(pilot_long$p, "s", 2)[,2]
# turn components to wide table
pilot_wide <- spread(pilot_long, question, data)
```


<h1> Within-Subject MANOVA </h1>

http://www.sthda.com/english/wiki/manova-test-in-r-multivariate-analysis-of-variance

```{r design}
# MANOVA test for design effects
res.man <-  manova(cbind(Aesthetic,Clarity,Professionalism,Trustworthiness) ~ design + Error(p), 
                  data =pilot_wide)
summary(res.man, test = "Pillai")
```

<h1> Power </h1>

The Pillai's value was entered into G*Power for power analysis,
There are 3 groups (Design: Cluttered, Decluttered, Focus), and 4 response variables (A,C,P,T)
Which has an effect size f^2 of 0.2058726.

This suggests a small-medium effect size.
https://www.statisticssolutions.com/membership-resources/member-profile/sample-size-power-analysis/write-up-generator-references/manova-groups/manova-2-levels-and-4-dependent-variables/


With alpha level= 0.05, at the current design, we have achieved 90.4% power. 

The ideal sample-size would be 60 (20 participants, 3 measures from each). That way we will have 95.28661% power at alpha level 0.05. 

<br>

<h1> Visualizing Results </h1>

```{r}
ggplot(pilot_wide, aes(designdummy,Aesthetic)) +
  geom_point()+
  geom_line(aes(group=p))+
  geom_smooth(method=lm,span=0.3)+
  labs(x="Design",
      y="Aesthetics Ratings") +
  facet_wrap(~topic)+
  scale_x_discrete(breaks=c("1","2","3"),
        labels=c("Cluttered", "Decluttered", "Focused"))+
  theme_minimal()

ggplot(pilot_wide, aes(designdummy,Clarity)) +
  geom_point()+
  geom_line(aes(group=p))+
  geom_smooth(method=lm,span=0.3)+
  labs(x="Design",
      y="Clarity Ratings") +
  facet_wrap(~topic)+
  scale_x_discrete(breaks=c("1","2","3"),
        labels=c("Cluttered", "Decluttered", "Focused"))+
  theme_minimal()

ggplot(pilot_wide, aes(designdummy,Professionalism)) +
  geom_point()+
  geom_line(aes(group=p))+
  geom_smooth(method=lm,span=0.3)+
  labs(x="Design",
      y="Professionalism Ratings") +
  facet_wrap(~topic)+
  scale_x_discrete(breaks=c("1","2","3"),
        labels=c("Cluttered", "Decluttered", "Focused"))+
  theme_minimal()

ggplot(pilot_wide, aes(designdummy,Trustworthiness)) +
  geom_point()+
  geom_line(aes(group=p))+
  geom_smooth(method=lm,span=0.3)+
  labs(x="Design",
      y="Trustworthiness Ratings") +
  facet_wrap(~topic)+
  scale_x_discrete(breaks=c("1","2","3"),
        labels=c("Cluttered", "Decluttered", "Focused"))+
  theme_minimal()
```

```{r functions, echo = FALSE}
pairwise.perm.manova <- function(resp,fact,test=c("Pillai","Wilks","Hotelling-Lawley","Roy","Spherical"),
  nperm=999,progress=TRUE,p.method="fdr") {
  call <- match.call()
  dname <- paste0(deparse(call$resp)," by ",deparse(substitute(fact)),"\n",nperm," permutations")
  fact <- factor(fact)
  if ("dist" %in% class(resp)) {
    fun.p <- function(i,j) {
	fact2 <- droplevels(fact[as.numeric(fact) %in% c(i,j)])
	resp2 <- as.matrix(resp)
	rows <- which(fact %in% levels(fact2))
	resp2 <- as.dist(resp2[rows,rows])
	vegan::adonis(resp2~fact2,permutations=nperm)$aov.tab[1,"Pr(>F)"]
    }
    multcomp <- pairwise.table(fun.p,levels(fact),p.adjust.method=p.method)
    method <- "permutation MANOVAs on a distance matrix"
  } else {
    if (nrow(resp)!=length(fact)) {
	stop(paste("'",deparse(substitute(resp)),"' and '",deparse(substitute(fact)),
	  "' lengths differ",sep=""))
    }
    test <- match.arg(test)
    if (!is.matrix(resp)) {resp <- as.matrix(resp)}
    if (!is.factor(fact)) {fact <- factor(fact)}
    fun.p <- function(i,j) {
	resp2 <- resp[as.numeric(fact) %in% c(i,j),]
	fact2 <- droplevels(fact[as.numeric(fact) %in% c(i,j)])
	perm.manova(resp2,fact2,test=test,nperm=nperm,progress)
    }
    multcomp <- pairwise.table(fun.p,levels(fact),p.adjust.method=p.method)
    method <- paste0("permutation MANOVAs (test: ",test,")")
  }
  result <- list(method=method,data.name=dname,p.value=multcomp,p.adjust.method=p.method)
  class(result) <- "pairwise.htest"
  return(result)
}

perm.manova <- function(resp,fact,test,nperm,progress) {
  manova.ref <- anova(lm(resp~fact),test=test)
  stat <- ifelse(test!="Spherical","approx F","F")
  F.ref <- manova.ref[2,stat]
  F.perm <- numeric(nperm+1)
  F.perm[1] <- F.ref
  if (progress) {pb <- txtProgressBar(min=0,max=100,initial=0,style=3)}
  for (i in 1:nperm) {
    manova.perm <- anova(lm(resp[sample(1:nrow(resp)),]~fact),test=test)
    F.perm[i+1] <- manova.perm[2,stat]
    if (progress) {setTxtProgressBar(pb,round(i*100/nperm,0))}
  }
  if (progress) {cat("\n")}
  pvalue <- length(which((F.perm+.Machine$double.eps/2) >= F.ref))/(nperm+1)
  return(pvalue)
}
```

<h1> Post-Hoc Analysis </h1>

Pairwise comparisons of the mean for design

```{r}
# pairwise.perm.manova(exp1_wide[,8:11],exp1_wide$design,nperm=49)
pairwise.perm.manova(pilot_wide[,8:11], pilot_wide$design, 
  test = c("Pillai"
#, "Wilks","Hotelling-Lawley", "Roy", "Spherical"
  ), 
  nperm = 999, 
  progress = TRUE, p.method = "bonferroni")
```

Visualize the pilot results on the quant ratings

```{r}
#detach("package:plyr", unload=TRUE) 

A <- pilot_wide[,c(1,2,8:11)]%>%
  group_by(design) %>%
  summarise(n = n(), 
            rating = mean(Aesthetic),
            se = sd(Aesthetic)/sqrt(n()),
            n = n,
            dimension = "Aesthetic")

C <- pilot_wide[,c(1,2,8:11)]%>%
  group_by(design) %>%
  summarise(n = n(), 
            rating = mean(Clarity),
            se = sd(Clarity)/sqrt(n()),
            n = n,
            dimension = "Clarity")

P <- pilot_wide[,c(1,2,8:11)]%>%
  group_by(design) %>%
  summarise(n = n(), 
            rating = mean(Professionalism),
            se = sd(Professionalism)/sqrt(n()),
            dimension = "Professionalism")

Tr <- pilot_wide[,c(1,2,8:11)]%>%
  group_by(design) %>%
  summarise(n = n(), 
            rating = mean(Trustworthiness),
            se = sd(Trustworthiness)/sqrt(n()),
            n = n,
            dimension = "Trustworthiness")

pilot_summary <- as.data.frame(rbind(A,C,P,Tr))

ggplot(pilot_summary, aes(design, rating, fill = design,
                          ymin = rating - se * 1.96, 
                          ymax = rating + se * 1.96)) +
  geom_bar(stat = "identity",
           width = 0.4)+
  # error bars
  geom_errorbar(width = 0.1,
                position = position_dodge(0.5)) + 
  facet_wrap(~dimension, nrow = 1) + 
  # label axis
  labs(x = "design",
       y = "rating") +
  theme_minimal()
```


```{r}
pilot_summary <- rbind(A, C, P, Tr)
pilot_summary %>%
  write.csv("pilot_summary.csv")
```

